### 2013-02-09 patchy-selection-paper.tex
/* Patchy Selection paper */

For simplicity we will assume that each of these patches has
the same size and geometry (i.e. same $E$). A particular patch adapts in parallel through an independent
instance of the $B$ mutation at rate $2 s_B \mu \rho A$.
While, if patches $1$ through $k$ are already occupied by
established copies of the $B$ allele, and these patches are at
distances $R_1,~\cdots,~R_k$ away from our patch, the rate of
adaptation through migration in our patch is 
\begin{equation}
\sum_{i=1}^{k} 2 s_B \rho E \exp(- |\sqrt{s_m} R_k/\sigma|}.
\end{equation}
Once again the compound parameter $2s_B \rho$ will function to
scale the times between events (parallel adaptation or the spread of a
migrant), and so is critical to the time-scale over which
adaptation occurs. However, this compound parameter again has no effect on
the final configuration of the pattern of which patches have adapted
in parallel versus have shared genetic basis to their adaptive
response to the poor environment.

@@

\section{Applications}

HbS

lava bed peromyscus

G6PD

>>>>

For simplicity we will assume that each of these patches has
the same size and geometry (i.e. same $E$). A particular patch adapts in parallel through an independent
instance of the $B$ mutation at rate $2 s_B \mu \rho A$.
While, if patches $1$ through $k$ are already occupied by
established copies of the $B$ allele, and these patches are at
distances $R_1,~\cdots,~R_k$ away from our patch, the rate of
adaptation through migration in our patch is 
\begin{equation}
\sum_{i=1}^{k} 2 s_B \rho E \exp(- |\sqrt{s_m} R_k/\sigma|).
\end{equation}
Once again the compound parameter $2s_B \rho$ will function to
scale the times between events (parallel adaptation or the spread of a
migrant), and so is critical to the time-scale over which
adaptation occurs. However, this compound parameter again has no effect on
the final configuration of the pattern of which patches have adapted
in parallel versus have shared genetic basis to their adaptive
response to the poor environment.

@@

\section{Applications} 
Hoekstra, Nachman, and colleagues have made an extensive study of coat color in the rock pocket mouse, \emph{Chaetodipus intermedius}, building on classic work by XXX. These mice live in the desert? through the American SouthWest and into Mexico. In the majority of their range they live on the light colored rocks, and have light pigmentation \citep[presumably an adaptation to visual-based predators][]{}. However, in some regions these mice live on dark colored substrates, including old lava flows, and have adapted to these patches in part through changes to a dark pigmentation. On one of these flows (Pinacate) an allele at the Mc1r locus is responsible for much of the change to a dark pelage \citep{Nachman:03}. This dark allele differs from the light allele by four amino acid changes - and has a dominant or partially dominant effect depending on the measure of coat color assessed. These lava flows are separated from each other by a range of distances, with some being separated from any other flow by hundreds of kilometers of light colored substrate. The Pinacate allele is not present in a number of other dark colored rock pocket mouse populations suggesting these populations have adapted in parallel. However, there is some evidence \citep{Hoekstra:05} that some close populations may have adapted by the spread of another dark allele by migration.

As can be seen from above a key parameter is $\sigma/\sqrt{s}$. \citep{Hoekstra:04} studied the frequency of the dark MC1R allele, and coat color phenotypes, at sites on the Pinacate lava flow and at two nearby light substrate sites. On the lava flow the dark MC1R allele is at $86\%$ frequency. At the Tule light substrate site, which is $\sim 12km$ from the flow, the dark MC1R allele was at $\sim 3\%$ frequency. At a greater distance from the lava ($XXX$km) the light colored substrate the dark MC1R was absent from a sample at the Christmas pass. While at the light substrate O'Neill site, which is $10$km from the flow on opposite side from Tule, the dark MC1R allele has a frequency of $\sim 34\%$.

I estimate that a characteristic length of 2.8km gives the frequency dropping from 50\% to ~1\% in this distance. So this doesn't seem so off. A characteristic length that is 1.4x gives 2.8\% from 50\% in 12km, which may be a little more accurate.

2) The frequency at O'Neill [another site off the lava, on opposite side from Tule]  is 9km from the lava and has a frequency of 34\% of the dark allele. I estimate that we need a sigma/sqrt(s) of ~28km (i.e. ten times the characteristic length) to give a drop from 50\% to 34\%.

[Obviously the cline isn't decaying from 50\%, the frequency of the light allele on the lava to be ~14%, we could put this in more carefully]
So it seems to me that a sigma/sqrt(s) of 3-30km seems to encompass a range of interesting parameters, and can be justified without too much trouble.

Using the dispersal distance of 0.28km [from marker recapture] and an s=0.01 [from paper] gives us sigma/sqrt(s)=2.8km
